Figures

### 2019-05-06 figures/04_nlcd-versus-cdl.Rmd
add r2 to cdl validation plot

ggplot(data = res, aes(x = nlcd, y = cdl)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1) +
  facet_wrap(~variable) +
  theme_minimal()
```

>>>>

get_r2 <- function(x, y){
  fit <- lm(y ~ x)
  round(broom::glance(fit)$r.squared, 2)
}

r2 <- data.frame(variable = c("ag", "pasture"), 
                 r2 = c(get_r2(dplyr::filter(res, variable == "ag")$cdl, 
                               dplyr::filter(res, variable == "ag")$nlcd), 
                        get_r2(dplyr::filter(res, variable == "pasture")$cdl, 
                               dplyr::filter(res, variable == "pasture")$nlcd)
                        ), stringsAsFactors = FALSE)
r2$r2 <- paste0("r2 = ", r2$r2)

ggplot(data = res, aes(x = nlcd, y = cdl)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1) +
  facet_wrap(~variable) +
  geom_text(data = r2, aes(x = 13, y = 75, label = r2)) +
  theme_minimal()
```
